\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-04 lang-design.tex
move a comment

Our plugin does allow the overriding of transparent definitions that are
explicitly marked as \lsti{Overridable} by the programmer.
Overriding is made safe by requiring that when an overridable field is
overridden, code whose type checking involves unfolding that field
should be overridden too.
We expect this feature to be used only occasionally.
We give an example in \cref{sec:coqexample}.

@@

\noindentparagraph{Composing families.} \EDJ{I feel this paragraph will cause more confusion---because it is inheritance judgement/linkage transformer being mixed in, not family itself. Conceptually not distinguishing family and linkage transfomer will make reader wonder what this magic black box here actually is}

Families can be readily reused to construct larger extensions that
\emph{mix in}~\cite{mixin-1990} the functionalities of the individual
families.
In \cref{fig:stlc-isorec-prod}, family "STLCFixIsorec" is declared as
an "STLC" extension that mixes in "STLCFix" and "STLCIsorec".
As a result, \lsti{STLCFixIsorec.typesafe} is readily the proof of the type-safety
theorem of an STLC equipped with fixpoints and iso-recursive types.

>>>>

Our plugin does allow the overriding of transparent definitions that are
explicitly marked as \lsti{Overridable} by the programmer.
Overriding is made safe by requiring that when an overridable field is
overridden, code whose type checking involves unfolding that field
should be overridden too.
We expect this feature to be used only occasionally.
Our case studies contain uses of overriding (\cref{sec:casestudies}).

@@

\noindentparagraph{Composing families.}

Families can be readily reused to construct larger extensions that
\emph{mix in}~\cite{mixin-1990} the functionalities of the individual
families.
In \cref{fig:stlc-isorec-prod}, family "STLCFixIsorec" is declared as
an "STLC" extension that mixes in "STLCFix" and "STLCIsorec".
As a result, \lsti{STLCFixIsorec.typesafe} is readily the proof of the type-safety
theorem of an STLC equipped with fixpoints and iso-recursive types.\EDJ{I feel this paragraph will cause more confusion---because it is inheritance judgement/linkage transformer being mixed in, not family itself. Conceptually not distinguishing family and linkage transfomer will make reader wonder what this magic black box here actually is}
